Approximation as Differentiation

### 2025-05-08 main/formal-structures.tex
Progress on properties of LatGal.

As sketched in \secref{introduction:galois-slicing}, for Galois slicing we require a setting where the
approximants of a point $x$ form a bounded lattice $(X, \meet, \join, \top, \bot)$, with least element $\bot$
representing the approximation that discards all information about $x$, greatest element $\top$ representing
the approximation that retains all information about $x$, and $\meet$ and $\join$ providing two canonical ways
to combine approximations. Thus rather than working in $\PosGal$, we define the following subcategory.

>>>>

As sketched in \secref{introduction:galois-slicing}, Galois slicing requires the approximants of a point $x$
to form a bounded lattice $(X, \meet, \join, \top, \bot)$, with least element $\bot$ representing the
approximation that discards all information about $x$, greatest element $\top$ representing the approximation
that retains all information about $x$, and $\meet$ and $\join$ providing two canonical ways to combine
approximations. Thus rather than working in $\PosGal$, we define the following subcategory.
